\pdfoutput=1 % only if pdf/png/jpg images are used
\documentclass[a4paper,10pt]{article}
%\documentclass[a4paper,10pt]{scrartcl}
%\documentclass[smallcondensed,referee]{svjour3}
\usepackage{geometry}
\geometry{a4paper,left=34mm,right=34mm, top=24mm, bottom=32mm}
%\geometry{a4paper}
\raggedbottom
\widowpenalty=10000
\clubpenalty=10000 
\usepackage{graphics}  
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage[amssymb]{SIunits}
%\usepackage[load-configurations=abbreviations,tight-spacing=true,separate-uncertainty,bracket-numbers = false]{siunitx} % JINST cannnot handle siunitx !!
\usepackage{nicefrac}
\usepackage[english]{babel}
\usepackage{lineno}
\usepackage{epstopdf}
\usepackage{stfloats}
%\usepackage{upgreek}
\usepackage{verbatim}
\usepackage{url}
\usepackage{xcolor}
%\usepackage{draftwatermark}
%\SetWatermarkScale{5}
\usepackage{setspace}


%general stuff 
\newcommand{\e}{\ensuremath{\mathnormal{e}}}
\newcommand{\h}{\ensuremath{\mathnormal{h}}}
\newcommand{\eV}{\ensuremath{\mathnormal{eV}}}
\newcommand{\cspeed}{\ensuremath{\mathnormal{c}}}

%tscope specific
\newcommand{\DESY}{\ensuremath{\textrm{DESY}}}
\newcommand{\Datura}{\ensuremath{\textrm{DATURA}}}
\newcommand{\Duranta}{\ensuremath{\textrm{DURANTA}}}
\newcommand{\Mimosa}{\ensuremath{\textrm{MIMOSA\,26}}}
\newcommand{\noise}{\ensuremath{\xi_{\textrm{n}}}}
\newcommand{\epsdut}{\ensuremath{\mathnormal{\varepsilon_{\textrm{DUT}}}}}
\newcommand{\epsmimo}{\ensuremath{\mathnormal{\varepsilon_{\textrm{M26}}}}}
\newcommand{\dz}{\ensuremath{\textrm{d}z}}
\newcommand{\dzdut}{\ensuremath{\textrm{d}z_{\textrm{DUT}}}}

%resolutions
\newcommand{\sigmap}{\ensuremath{\sigma_{\textrm{pointing}}}}
\newcommand{\sigmatu}{\ensuremath{\sigma_{\textrm{t,u}}}}
\newcommand{\sigmatb}{\ensuremath{\sigma_{\textrm{t,b}}}}
\newcommand{\sigmat}{\ensuremath{\sigma_{\textrm{t}}}}
\newcommand{\sigmapGBL}{\ensuremath{\sigma_{\textrm{p,GBL}}}}
\newcommand{\sigmameas}{\ensuremath{\sigma_{\textrm{meas}}}}
\newcommand{\sigmadut}{\ensuremath{\sigma_{\textrm{DUT}}}}
\newcommand{\sigmai}{\ensuremath{\sigma_{\textrm{int}}}}
\newcommand{\sigmam}{\ensuremath{\sigma_{\textrm{M26}}}}
\newcommand{\sigmahat}{\ensuremath{\hat{\sigma}_{\textrm{int}}}}

%positions
\newcommand{\zdut}{\ensuremath{z_{\textrm{DUT}}}}
\newcommand{\zzz}{\ensuremath{z_{3}}}

%residuals
\newcommand{\rbiased}{\ensuremath{r_{\textrm{b}}}}
\newcommand{\runbiased}{\ensuremath{r_{\textrm{u}}}}
\newcommand{\rhat}{\ensuremath{\hat{r}_{\textrm{b}}}}
\newcommand{\pb}{\ensuremath{p_{\textrm{b}}}}


%software
\newcommand{\eudet}{\ensuremath{\textrm{EUDET}}}
\newcommand{\rawdataevent}{RawDataEvent }
\newcommand{\rawdataevents}{RawDataEvents }
\newcommand{\eudaq}{\ensuremath{\textrm{EUDAQ}}}
\newcommand{\EUTelescope}{\ensuremath{\textrm{EUTelescope}}}

%conditional compilation
\newcommand*{\notFOREPJ}{}%

%linenumbers
\setpagewiselinenumbers
\modulolinenumbers[5]

\ifdefined\notFOREPJ
\else
\doublespacing
\fi

\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
  \vspace*{10mm}
  \textbf{\huge\sffamily\@title}
  \vspace{5mm}
   
  \large \@author
\end{flushleft}\egroup
}
\def\@xfootnote[#1]{%
  \protected@xdef\@thefnmark{#1}%
  \@footnotemark\@footnotetext}
\makeatother

%\setlength\extrarowheight{5pt}
\renewcommand{\arraystretch}{1.25}


%\keywords{Pixel, CMOS, Beam telescope, resolution, tracker} % need to be specified during submission

\begin{document}
\linenumbers


%DESY 6
%D. Eckstein, 				doris.eckstein@desy.de
%T. Eichhorn, 				thomas.eichhorn@desy.de
%I. Gregor,				ingrid.gregor@desy.de
%C. Muhl,				carsten.muhl@desy.de
%H. Jansen, 				hendrik.jansen@desy.de
%R. Peschke,				Richard.Peschke@desy.de
%S. Spannagel,				simon.spannagel@desy.de

% Uni of Bristol 1
%D. G. Cussansm				David.Cussans@bristol.ac.uk

%DPNC 2
%E. Corrin,		SwiftKey	emlyn.corrin@gmail.com
%D. Hass, 		SRON: 		D.Haas@sron.nl

%IPHC Strasbourg, France 3
%Mark Winter				marc.winter@iphc.cnrs.fr
%Mathieu Goffe				mathieu.goffe@iphc.cnrs.fr
%Gilles Claus				gilles.claus@iphc.cnrs.fr 

%INFN Como 1
%Antonio Bulgheroni, 	KIT		antonio.bulgheroni@gmail.com

%Ex-DESY: 5
%H. Perrey, 				hanno@perrey.info
%Philipp Roloff,	CERN 		philipp.roloff@cern.ch
%I. Rubinskiy,		CFEl/CUIigor	igor.rubinskiy@cfel.de

\title{Performance of the EUDET-type\\ beam telescopes}
\author{
H.~Jansen${}^{\textrm{a,}}$\footnote[*]{Corresponding author: hendrik.jansen@desy.de},
S.~Spannagel${}^{\textrm{a}}$, 
J.~Behr${}^{\textrm{a,}}$\footnote{Now at ??},
A.~Bulgheroni${}^{\textrm{b,}}$\footnote{Now at KIT, Karlsruhe, Germany},
G.~Claus${}^{\textrm{c}}$,
E.~Corrin${}^{\textrm{d,}}$\footnote{Now at SwiftKey, London, UK},
D.~G.~Cussans${}^{\textrm{e}}$,
J.~Dreyling-Eschweiler${}^{\textrm{a}}$, 
D.~Eckstein${}^{\textrm{a}}$, 
T.~Eichhorn${}^{\textrm{a}}$, 
M.~Goffe${}^{\textrm{c}}$,
I.~M.~Gregor${}^{\textrm{a}}$, 
D.~Haas${}^{\textrm{d,}}$\footnote{Now at SRON, Utrecht, Netherlands},
C.~Muhl${}^{\textrm{a}}$,
H.~Perrey${}^{\textrm{a,}}$\footnote{Now at Lund University, Sweden}, 
R.~Peschke${}^{\textrm{a}}$, 
P.~Roloff${}^{\textrm{a,}}$\footnote{Now at CERN, Geneva, Switzerland}, 
I.~Rubinskiy${}^{\textrm{a,}}$\footnote{Now at CFEL, Hamburg, Germany}, 
M.~Winter${}^{\textrm{c}}$\\
\vspace{3mm}
${}^{\textrm{a}}$ Deutsches Elektronen-Synchrotron DESY, Hamburg, Germany\\
${}^{\textrm{b}}$ INFN Como, Italy\\
${}^{\textrm{c}}$ IPHC, Strasbourg, France\\
%${}^{\textrm{c}}$ D\'epartement de physique nucl\'eaire et corpusculaire, University of Geneva, Switzerland\\
${}^{\textrm{d}}$ DPNC, University of Geneva, Switzerland\\
${}^{\textrm{e}}$ University of Bristol, UK
}
\maketitle


%-------------------
% \title{The EUDET-type Beam Telescopes}
% \author{
% H.~Jansen${}^{\textrm{a,}}$\thanks{Corresponding author: hendrik.jansen@desy.de}\,\,, 
% A.~Bulgheroni${}^{\textrm{b,}}$\thanks{Now at KIT, Karlsruhe, Germany},
% G.~Claus${}^{\textrm{c}}$,
% E.~Corrin${}^{\textrm{d,}}$\thanks{Now at Swiftkey, London, UK}\,\,,
% D.~G.~Cussans${}^{\textrm{e}}$,
% D.~Eckstein${}^{\textrm{a}}$, T. Eichhorn${}^{\textrm{a}}$, M. Goffe${}^{\textrm{c}}$,
% I.~M.~Gregor${}^{\textrm{a}}$, 
% D.~Haas${}^{\textrm{d,}}$\thanks{Now at SRON, Utrecht, Netherlands}\,\,,
% %  A. Kravchenko${}^{\textrm{a,}}$\thanks{Now at }\,\,, 
% H.~Perrey${}^{\textrm{a,}}$\thanks{Now at ESS, Lund, Sweden}\,\,, 
% R.~Peschke${}^{\textrm{a}}$, 
% P.~Roloff${}^{\textrm{a,}}$\thanks{Now at CERN, Geneva Switzerland}\,\,, 
% I.~Rubinskiy${}^{\textrm{a,}}$\thanks{Now at CFEl, Hamburg, Germany}\,\,\,\,, 
% S.~Spannagel${}^{\textrm{a}}$, 
% M. Winter${}^{\textrm{c}}$\\
% \vspace{3mm}
% ${}^{\textrm{a}}$ Deutsches Elektronen-Synchrotron DESY, Hamburg, Germany\\
% ${}^{\textrm{b}}$ INFN Como, Italy\\
% ${}^{\textrm{c}}$ IPHC, Strasbourg, France\\
% %${}^{\textrm{c}}$ D\'epartement de physique nucl\'eaire et corpusculaire, University of Geneva, Switzerland\\
% ${}^{\textrm{d}}$ DPNC, University of Geneva, Switzerland\\
% ${}^{\textrm{e}}$ University of Bristol, UK
% }
% \maketitle
%----------------

\begin{abstract}
\noindent
Test beam measurements at the test beam facilities of DESY have been conducted to characterise the performance of the EUDET-type beam telescopes originally developed within the $\eudet$ project. 
The beam telescopes are equipped with six sensor planes using $\Mimosa$ monolithic active pixel devices. 
A programmable Trigger Logic Unit provides trigger logic and time stamp information on particle passage. 
Both data acquisition framework and offline reconstruction software packages are available. 
User devices are easily integrable into the data acquisition framework via predefined interfaces.
 
The biased residual distribution is studied as a function of the beam energy, plane spacing and sensor threshold. 
Its width at the two centre pixel planes using all six planes for tracking in a 6\,GeV electron/positron-beam is measured to be $(2.88\,\pm\,0.08)\,\upmu\meter$.
Iterative track fits using the formalism of General Broken Lines are performed to estimate the intrinsic resolution of the individual pixel planes. 
The mean intrinsic resolution over the six sensors used is found to be $(3.24\,\pm\,0.09)\,\upmu\meter$.
With a 5\,GeV electron/positron beam, the track resolution halfway between the two inner pixel planes using an equidistant plane spacing of 20\,mm is estimated to $(1.78\,\pm\,0.03)\,\upmu\meter$
 assuming the measured intrinsic resolution. 
Towards lower beam energies the track resolution deteriorates due to increasing multiple scattering. 
Threshold studies show an optimal working point of the $\Mimosa$ sensors at a sensor threshold of between five and six times their RMS noise. 
Measurements at different plane spacings are used to calibrate the amount of multiple scattering in the material traversed
 and allow for corrections to the predicted angular scattering for electron beams. 
\end{abstract}

\ifdefined\notFOREPJ
\tableofcontents
\else
\fi


\section{Introduction}
\label{sec:intro}
\ifdefined\notFOREPJ
\input{content/intro}
\else
\input{intro}
\fi

\section{Beamlines}
\label{sec:beamlines}
\ifdefined\notFOREPJ
\input{content/beam_lines}
\else
\input{beam_lines}
\fi

\section{Components of the EUDET-type beam telescopes}
\label{sec:tscope}
\ifdefined\notFOREPJ
\input{content/tscope}
\else
\input{tscope}
\fi

\section{The EUDAQ data acquisition framework}
\label{sec:eudaq}
\ifdefined\notFOREPJ
\input{content/eudaq}
\else
\input{eudaq}
\fi

\section{Offline analysis and reconstruction using EUTelescope}
\label{sec:offline}
\ifdefined\notFOREPJ
\input{content/offline}
\else
\input{offline}
\fi

\section{Track resolution studies}
\label{sec:trackres}
\ifdefined\notFOREPJ
\input{content/track_resolution}
\else
\input{track_resolution}
\fi

\section{Considerations for DUT integrations}
\label{sec:dutintegration}
\ifdefined\notFOREPJ
\input{content/dutintegration}
\else
\input{dutintegration}
\fi

\section{Conclusion}
\label{sec:conclusion}
\ifdefined\notFOREPJ
\input{content/conclusion}
\else
\input{conclusion}
\fi

\ifdefined\notFOREPJ
\else
\section*{Data and materials}
The datasets supporting the conclusions of this article are available in the ?? repository, http:// ftp:// ??.
The software used is available in the github repository, https://github.com/simonspa/eutelescope/, branch \textit{scattering} and https://github.com/simonspa/resolution-simulator.
For the analysis, these specific tags have been used: \cite{} and \cite{spannagel_2016_48795}.

\section*{Competing interests}
The authors declare that they have no competing interests.
\fi

\section*{Acknowledgements}
We are indebted to Claus Kleinwort for his counsel and numerous discussions. 
Also, we would like to thank Ulrich K\"otz.
The test beam support at DESY is highly appreciated. 
This work was supported by the Commission of the European Communities under the FP7 Structuring the European Research Area, contract number RII3-026126 (EUDET). 
Furthermore, strong support from the Helmholtz Association and the BMBF is acknowledged.
%contract number RII3-CT-2006-026126.
%Funding agencies AIDA, EUDET

\small
\bibliographystyle{IEEEtran}
\ifdefined\notFOREPJ
\bibliography{bibtex/refs}
\else
\bibliography{refs}
\fi

\end{document}


