%mechanic
Mechanically, a DUT can be integrated into the DESY-type beam telescope at various positions. 
However, a micrometer precision $xy\phi$-stage, placed between the up- and downstream arm, is available for translation over the acceptance region and rotation of the DUT~\cite{Mimosa-twiki}.
At this position, the maximum DUT size is 500\,mm.

%trigger and daq sw
User DAQ systems are integrated the same way as the beam telescope DAQ itself using either the RJ45 or the LEMO interface, cf.~section~\ref{sec:tdaq}.
All integrated systems use the same handshake mode.
Therefore, all systems have to de-assert their busy before the next trigger is issued in case the simple or the normal handshake mode is employed. 
For the integration of the DUT data stream with EUDAQ, a producer capable of receiving commands by the Run Control and sending data to the $\eudaq$ Data Collector is necessary,
 as described in section~\ref{sec:eudaq}.
A dedicated alignment run prior to the installation of the DUT is advantageous during the data reconstruction, especially for larger $\epsdut$.

%eutelescope
The data stemming from the alignment run is used for the alignment of the telescope planes in the early stage of the reconstruction. 
With a proper alignment at hand, runs including a DUT are to be analysed subsequently in order to align the DUT with respect to the beam telescope. 
The reconstructed tracks are then used to characterise the DUT, i.e.\ measure its intrinsic resolution or its detection efficiency. 

With increasing $\epsdut$, and thus multiple scattering within the DUT, the choice of the tracking processor needs further consideration. 
In general, a GBL fit produces tracks with a lower $\chi^2$ compared to straight line fits,
 as kinks at the possibly thick DUT and also at the $\Mimosa$ planes themselves are not allowed for in the straight line fit.
Therefore, using GBL for track fitting is recommended. 
% The inclusion of downstream planes using straight line fits might significantly deteriorate the resolution,
If straight line fitting is used nonetheless, a fit using only the upstream planes might result in a narrower unbiased residual width, compared to a fit that includes the downstream planes. 
This is due to a bias of the extrapolated tracks at the DUT by the downstream planes after passing traversing material. 
For comparison, in a narrow \textit{user configuration} using a 5\,GeV electron/positron beam, the pointing resolution of the DESY-type beam telescope at the DUT using GBL is $1.83\,\upmu\meter$. 
The optimal configuration using only the upstream planes is a wide configuration with $\dz = 150\,\milli\meter$,
 and the achievable pointing resolution is above $3.88\,\upmu\meter$. 
Hence, using only the upstream planes deteriorates the resolution by more than $2\,\upmu\meter$.

A web tool comprising compatible results in comparison with the GBL calculations is available~\cite{webtool}.